---
title: "MaxEnt Toolbox"
author: "Oakology"
date: "January 11, 2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown Script performs all the pre-processing of the data files for input into MaxEnt. Choose a scenario to run all the data processing for that scenario. Also be sure to turn on (remove the #) for a writing of rasters, csvs, or shapefiles, in order to have them run and saved. They are currently coded out so that they will not continuously overwrite previously compiled scenarios. Also if creating a new scenario, be sure to add it to the scenario options below and to add the appropriate folder structure for that scenario for where all outputs are to be written.

#Scenario Selection

```{r extent_selection}

#Change scenario
scenario<-"sca_270m"

#Options:
#allislands_270m
#ni_270m
#sca_270m
#sca_int_270m
#scr_270m
#sri_270m
#sri_adultyoung_270m
#sri_seedsap_270m
#scr_foginc_270m
#scr_fogdec_270m
#sri_foginc_270m
#sri_fogdec_270m
#scr_fogelev_270m
#sri_fogelev_270m
#scr_fogconstant_270m
#sri_fogconstant_270m
#MainlandCA

```


#Load Packages

```{r packages, message=FALSE}

#If packages missing use install.packages("packagename")
library(tidyverse)
library(sf)
library(raster)
library(sp)
library(rgdal)
library(tools)


```


#Extent

```{r extent}

#Create scenario extent that will be used throughout the rest of the processes, based off the minimum BCM data available as well as the Channel Island CUSP outlines

#If else statements for scenarios: read in the correct data for each scenario
if (scenario=="allislands_270m"){
  #All Islands
  scenario_extent<-read_sf("G:/data/islands/all_islands/extent/allislandsoutline.shp")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="ni_270m"){
  #Northern Islands
  scenario_extent<-read_sf("G:/data/islands/all_islands/ni_outline/ni_outline.shp")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="scr_270m"|scenario=="scr_foginc_270m"|scenario=="scr_fogdec_270m"|scenario=="scr_fogelev_270m"|scenario=="scr_fogconstant_270m"){
  #Santa Cruz
  scenario_extent<-read_sf("G:/data/islands/scr/scr_extent/scr_extent.shp")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="sri_270m"|scenario=="sri_adultyoung_270m"|scenario=="sri_seedsap_270m"|scenario=="sri_foginc_270m"|scenario=="sri_fogdec_270m"|scenario=="sri_fogelev_270m"|scenario=="sri_fogconstant_270m"){
  #Santa Rosa
  scenario_extent<-read_sf("G:/data/islands/sri/sri_extent/sri_extent.shp")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="sca_270m"){
  #Santa Catalina
  scenario_extent<-read_sf("G:/data/islands/sca/sca_extent/sca_extent.shp")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="sca_int_270m"){
  #Santa Catalina Interpolated
  scenario_extent<-read_sf("G:/data/islands/sca/sca_extent/sca_extent.shp")
  min_data<-raster("G:/data/climate/GIS_Input_SCAInterpolated/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="MainlandCA"){
  #Mainland CA
  scenario_extent<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else
  print ("No Scenario Selected")

#Turn the below on if you want to rewrite the extent rasters
# cropped <- crop(min_data, extent(scenario_extent)) #Crop to extent of outlines
# scen_extent <- mask(cropped, scenario_extent) #Mask to the exact island outline(s)
# extent(scen_extent)<-round(extent(scen_extent),1) #Rerun with rounded extent so extents same decimal amount
# writeRaster(scen_extent, filename=paste0("G:/data/islands/MaxEnt/Extent/", scenario, ".tif"), overwrite=TRUE)#write extent raster


#Extent will be used throughout Script. Will call in the extent each time just to be careful.

```


#Oak Combined and Individual 

```{r oakpoints}

#Read in Oak Points
sca_oaks<-read_sf("G:/data/islands/sca/Quertome/SCAOakPoints_AEA.shp")
sri_oaks<-read_sf("G:/data/islands/sri/OakPoint/SRI_OakPoints_Updated.shp")
scr_oaks<-read_sf("G:/data/islands/scr/OakPoint/SCR_OakPoints_Updated.shp")


#If else statements for scenarios: read in the correct data for each scenario
if (scenario=="allislands_270m"|scenario=="MainlandCA"){
  #All Islands or Mainland CA
  sca_xy<-st_coordinates(sca_oaks)
  sri_xy<-st_coordinates(sri_oaks)
  scr_xy<-st_coordinates(scr_oaks)
  all_oaks<-rbind(sca_xy[,1:2],sri_xy[,1:2],scr_xy[,1:2])
}else if (scenario=="ni_270m"){
  #Northern Islands
  sri_xy<-st_coordinates(sri_oaks)
  scr_xy<-st_coordinates(scr_oaks)
  all_oaks<-rbind(sri_xy[,1:2],scr_xy[,1:2])
}else if (scenario=="scr_270m"|scenario=="scr_foginc_270m"|scenario=="scr_fogdec_270m"|scenario=="scr_fogelev_270m"|scenario=="scr_fogconstant_270m"){
  #Santa Cruz
  scr_xy<-st_coordinates(scr_oaks)
  all_oaks<-scr_xy[,1:2]
}else if (scenario=="sri_270m"|scenario=="sri_foginc_270m"|scenario=="sri_fogdec_270m"|scenario=="sri_fogelev_270m"|scenario=="sri_fogconstant_270m"){
  #Santa Rosa
  sri_xy<-st_coordinates(sri_oaks)
  all_oaks<-sri_xy[,1:2]
}else if (scenario=="sca_270m"|scenario=="sca_int_270m"){
  #Santa Catalina and Santa Catalina Interpolated
  sca_xy<-st_coordinates(sca_oaks)
  all_oaks<-sca_xy[,1:2]
}else if (scenario=="sri_adultyoung_270m"){
  #Santa Rosa Adult and Young
  sri_ay<-subset(sri_oaks, sri_oaks$Age=="adult"|sri_oaks$Age=="young") #Fix this so it works
  sri_xy<-st_coordinates(sri_ay)
  all_oaks<-sri_xy[,1:2]
}else if (scenario=="sri_seedsap_270m"){
  #Santa Rosa Seedling and Saplings
  sri_ay<-subset(sri_oaks, sri_oaks$Age=="seedling"|sri_oaks$Age=="sapling") #Fix this so it works
  sri_xy<-st_coordinates(sri_ay)
  all_oaks<-sri_xy[,1:2]
}else
  print ("No Scenario Selected")

#Make Oak Point CSV based on selected oak points
alloaks<-as.data.frame(all_oaks)
alloaks$Species<-"Quercus tomentella"
Oaks<-alloaks[,c(3,1,2)]
oak_fn<-paste0("G:/data/islands/MaxEnt/MEInputOak/", scenario,"/OakPoints.csv")
#Turn on write csv to write out the oak points
#write.csv(Oaks, oak_fn, row.names=FALSE) 



```



#Climate  

```{r climate}

if (scenario=="sca_int_270m"){
  #Santa Catalina Interpolated: Made by KrigingCatalina_AllBCM.Rmd
  clim_dirs<-list.dirs(path="G:/data/climate/GIS_Input_SCAInterpolated", full.names=T, recursive=F)
}else
clim_dirs<-list.dirs(path="G:/data/climate/GISModel_Input", full.names=T, recursive=F)

#Call in appropriate extent
scen_extent<-raster(paste0("G:/data/islands/MaxEnt/Extent/", scenario, ".tif"))
crs(scen_extent)<-CRS('+init=epsg:3310') 
 
for (clim in clim_dirs){
  #print (clim) #For loop through climate projections
  clim_vars<-list.files(clim, pattern='tif$', full.names=TRUE )
  for (climvar in clim_vars){
    #print (climvar)#For loop through climate variables
    clim_ras<-raster(climvar)
    crs(clim_ras)<-CRS('+init=epsg:3310')
    
    if(scenario=="MainlandCA"){
      climate_new<- resample(clim_ras, scen_extent, "ngb")
    }else
      climate_new<-clim_ras
    
    clim_crop <- crop(climate_new, extent(scen_extent)) #Crop to extent of outlines
    climate <- mask(clim_crop, scen_extent) #Mask to the exact island outline(s)
    extent(climate)<-round(extent(climate),1) #Rerun with rounded extent so extents same decimal amount
    clim_name<-file_path_sans_ext(basename(climvar))
    fn <- paste0("G:/data/climate/MEInput/", scenario, "/", basename(clim), "/", clim_name, ".asc")
    #Uncode write raster if you want the raster to be written
    #writeRaster(climate,fn,format="ascii",overwrite=T)
  }#End for loop through climate variables
}#End for loop through climate projections



```



#Island

```{r island}


if (scenario!="MainlandCA"){

  #Set final directory
island_fn<-paste0("G:/data/islands/MaxEnt/MEInput/", scenario, "/")
#Call in appropriate extent
scen_extent<-raster(paste0("G:/data/islands/MaxEnt/Extent/", scenario, ".tif"))
crs(scen_extent)<-CRS('+init=epsg:3310') 


#Soils
  soilshp<-read_sf("G:/data/islands/all_islands/Soil/soils_AEA.shp")
  ext<-extent(scen_extent)
  gridsize <- 270
  soilr <- raster(ext, res=gridsize)
  soilras <- rasterize(soilshp, soilr, field = 'MapUnit')
  crs(soilras)<-CRS('+init=epsg:3310')
  soil_crop <- crop(soilras, extent(scen_extent)) #Crop to extent of outlines
  soils <- mask(soil_crop, scen_extent) #Mask to the exact island outline(s)
  extent(soils)<-round(extent(soils),1)
  #Uncode write raster if you want the raster to be written
  #writeRaster(soils,paste0(island_fn, "soilclasses.asc"),format="ascii",overwrite=T)
  

#Vegetation: Made by VegetationMapGrouping.Rmd
  #SCR
    scr_vegpshp<-read_sf("G:/data/islands/scr/SCRVegMapClass/SCRVegMapClass.shp")
    scr_vegr <- raster(extent(scen_extent), res=270)
    scr_vegras <- rasterize(scr_vegpshp, scr_vegr, field = 'Value')
    crs(scr_vegras)<-CRS('+init=epsg:3310')
  #NI
    ni_vegpshp<-read_sf("G:/data/islands/all_islands/Channel_Islands_Veg_Map_2017/NIVegMapClass/NIVegMapClass.shp")
    ni_vegr <- raster(extent(scen_extent), res=270)
    ni_vegras <- rasterize(ni_vegpshp, ni_vegr, field = 'Value')
    crs(ni_vegras)<-CRS('+init=epsg:3310')
  #SCA
    sca_vegpshp<-read_sf("G:/data/islands/sca/SCAVegMapClass/SCAVegMapClass.shp")
    sca_vegr <- raster(extent(scen_extent), res=270)
    sca_vegras <- rasterize(sca_vegpshp, sca_vegr, field = 'Value')
    crs(sca_vegras)<-CRS('+init=epsg:3310')
  #Merge to New Raster
    all_veg<-merge(scr_vegras, ni_vegras, sca_vegras)
    veg_crop <- crop(all_veg, extent(scen_extent)) #Crop to extent of outlines
    veg <- mask(veg_crop, scen_extent) #Mask to the exact island outline(s)
    extent(veg)<-round(extent(veg),1)
  #Uncode write raster if you want the raster to be written
    #writeRaster(veg,paste0(island_fn, "veg.asc"),format="ascii",overwrite=T)
    
    
#DEM
  ai_dem<-raster("G:/data/islands/all_islands/DEM/ai_dem270.tif")
  scr_dem<-raster("G:/data/islands/all_islands/DEM/scr_dem270.tif")
  sri_dem<-raster("G:/data/islands/all_islands/DEM/sri_dem270.tif")
  smi_dem<-raster("G:/data/islands/all_islands/DEM/smi_dem270.tif")
  sca_dem<-raster("G:/data/islands/sca/DEM/sca_dem_alb/sca_dem_alb270.tif")
  all_dem<-merge(ai_dem, scr_dem, sri_dem, smi_dem, sca_dem, tolerance=0.5)#Accepts different origins
  #all_dem<-raster("G:/data/islands/all_islands/DEM/all_dem270.tif") #Combined all DEMS at 270 in GIS with mosaic to new raster because much quicker and save across all projects
  all_dem_new <- resample(all_dem, scen_extent, "ngb")
  #Figure out cropping and masking issue 
  dem_crop <- crop(all_dem_new, scen_extent) #Crop to extent of outlines
  dem <- mask(dem_crop, scen_extent) #Mask to the exact island outline(s)
  extent(dem)<-round(extent(dem),1)
#Uncode write raster if you want the raster to be written
  #writeRaster(dem,paste0(island_fn, "DEM.asc"),format="ascii",overwrite=T)

  #Slope and Aspect
  all_terrain<-terrain(dem, opt=c('slope', 'aspect'), unit='degrees')
  slope<-all_terrain$slope
  aspect<-all_terrain$aspect
#Uncode write raster if you want the raster to be written
  #writeRaster(slope,paste0(island_fn, "slope.asc"),format="ascii",overwrite=T)
  #writeRaster(aspect,paste0(island_fn, "aspect.asc"),format="ascii",overwrite=T)

}else
  print ("Mainland CA needs data") #data not currently available for Mainland
  
  
```



#Fog

```{r fog}

scen_extent<-raster(paste0("G:/data/islands/MaxEnt/Extent/", scenario, ".tif"))
crs(scen_extent)<-CRS('+init=epsg:3310') 

#If else statements for scenarios: read in the correct data for each scenario
if (scenario=="scr_foginc_270m"){
  #Future fog changed by a percent (20%) Inc/Dec for SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/scr_allfog_270.tif")
  future_fog_10_40<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SCR/scr_All_increase045.tif")
  future_fog_40_70<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SCR/scr_All_increase135.tif")
  future_fog_70_100<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SCR/scr_All_increase225.tif")
  
}else if (scenario=="scr_fogdec_270m"){
  #Future fog changed by a percent (20%) Inc/Dec for SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/scr_allfog_270.tif")
  future_fog_10_40<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SCR/scr_All_decrease045.tif")
  future_fog_40_70<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SCR/scr_All_decrease135.tif")
  future_fog_70_100<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SCR/scr_All_decrease225.tif")

}else if (scenario=="sri_foginc_270m"){
  #Future fog changed by a percent (20%) Inc/Dec for SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/sri_allfog_270.tif")
  future_fog_10_40<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SRI/sri_All_increase045.tif")
  future_fog_40_70<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SRI/sri_All_increase135.tif")
  future_fog_70_100<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SRI/sri_All_increase225.tif")

}else if (scenario=="sri_fogdec_270m"){
  #Future fog changed by a percent (20%) Inc/Dec for SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/sri_allfog_270.tif")
  future_fog_10_40<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SRI/sri_All_decrease045.tif")
  future_fog_40_70<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SRI/sri_All_decrease135.tif")
  future_fog_70_100<-raster("G:/data/climate/Fog/Fog_270/PercentChange/SRI/sri_All_decrease225.tif")

}else if (scenario=="scr_fogelev_270m"){
  #Future Fog Elevation (+-20%): SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/scr_allfog_270.tif")
  future_fog_10_40<-raster("G:/data/climate/Fog/Fog_270/Elevation/SCR/scr_all_elevation045.tif")
  future_fog_40_70<-raster("G:/data/climate/Fog/Fog_270/Elevation/SCR/scr_all_elevation135.tif")
  future_fog_70_100<-raster("G:/data/climate/Fog/Fog_270/Elevation/SCR/scr_all_elevation225.tif")
  
}else if (scenario=="sri_fogelev_270m"){
  #Future Fog Elevation (+-20%): SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/sri_allfog_270.tif")
  future_fog_10_40<-raster("G:/data/climate/Fog/Fog_270/Elevation/SRI/sri_all_elevation045.tif")
  future_fog_40_70<-raster("G:/data/climate/Fog/Fog_270/Elevation/SRI/sri_all_elevation135.tif")
  future_fog_70_100<-raster("G:/data/climate/Fog/Fog_270/Elevation/SRI/sri_all_elevation225.tif")

}else if (scenario=="scr_fogconstant_270m"){
  #Current fog level constant across all future projections
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/scr_allfog_270.tif")
  future_fog_10_40<-raster("G:/data/climate/Fog/Fog_270/Historic/scr_allfog_270.tif")
  future_fog_40_70<-raster("G:/data/climate/Fog/Fog_270/Historic/scr_allfog_270.tif")
  future_fog_70_100<-raster("G:/data/climate/Fog/Fog_270/Historic/scr_allfog_270.tif")
    
}else if (scenario=="sri_fogconstant_270m"){
  #Current fog level constant across all future projections
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/sri_allfog_270.tif")
  future_fog_10_40<-raster("G:/data/climate/Fog/Fog_270/Historic/sri_allfog_270.tif")
  future_fog_40_70<-raster("G:/data/climate/Fog/Fog_270/Historic/sri_allfog_270.tif")
  future_fog_70_100<-raster("G:/data/climate/Fog/Fog_270/Historic/sri_allfog_270.tif")
  
}else
  print ("No Fog Data Available")


if (scenario=="scr_foginc_270m"|scenario=="scr_fogdec_270m"|scenario=="sri_foginc_270m"|scenario=="sri_fogdec_270m"|scenario=="scr_fogelev_270m"|scenario=="sri_fogelev_270m"|scenario=="scr_fogconstant_270m"|scenario=="sri_fogconstant_270m"){
  
#Goes through the climate folders and inserts current into historic and future into different climate projections
  
  #Resample
  current_fog_new <- resample(current_fog, scen_extent, "ngb")
  future_fog_1040_new <- resample(future_fog_10_40, scen_extent, "ngb")
  future_fog_4070_new <- resample(future_fog_40_70, scen_extent, "ngb")
  future_fog_70100_new <- resample(future_fog_70_100, scen_extent, "ngb")
  #Crop and Mask
  current_fog_crop <- crop(current_fog_new, scen_extent) #Crop to extent of outlines
  current_fog_mask <- mask(current_fog_crop, scen_extent) #Mask to the exact island outline(s)
  future_fog_1040_crop <- crop(future_fog_1040_new, scen_extent) #Crop to extent of outlines
  future_fog_1040_mask <- mask(future_fog_1040_crop, scen_extent) #Mask to the exact island outline(s)
  future_fog_4070_crop <- crop(future_fog_4070_new, scen_extent) #Crop to extent of outlines
  future_fog_4070_mask <- mask(future_fog_4070_crop, scen_extent) #Mask to the exact island outline(s)
  future_fog_70100_crop <- crop(future_fog_70100_new, scen_extent) #Crop to extent of outlines
  future_fog_70100_mask <- mask(future_fog_70100_crop, scen_extent) #Mask to the exact island outline(s)
  #Extent
  extent(current_fog_mask)<-round(extent(current_fog_mask),1)
  extent(future_fog_1040_mask)<-round(extent(future_fog_1040_mask),1)
  extent(future_fog_4070_mask)<-round(extent(future_fog_4070_mask),1)
  extent(future_fog_70100_mask)<-round(extent(future_fog_70100_mask),1)
  
  clim_dirs<-list.dirs(path="G:/data/climate/GISModel_Input", full.names=T, recursive=F)
    for (clim in clim_dirs){
      #print (clim) #For loop through climate projections
      if(basename(clim)=="historic"|basename(clim)=="historic_1921_1950"|basename(clim)=="historic_1951_1980"){
        
        current_fog_fn <- paste0("G:/data/climate/MEInput/", scenario, "/", basename(clim), "/fog.asc")
      #Uncode write raster if you want the raster to be written
        #writeRaster(current_fog_mask,current_fog_fn,format="ascii",overwrite=T)
        
      }else if (basename(clim)=="CCSM4_rcp85_2010_2039"|basename(clim)=="MIROC_rcp45_2010_2039"|basename(clim)=="MIROC_rcp85_2010_2039"|basename(clim)=="MPI_rcp45_2010_2039"){
        
        future_fog_fn <- paste0("G:/data/climate/MEInput/", scenario, "/", basename(clim), "/fog.asc")
      #Uncode write raster if you want the raster to be written
        #writeRaster(future_fog_1040_mask,future_fog_fn,format="ascii",overwrite=T)
        
      }else if (basename(clim)=="CCSM4_rcp85_2040_2069"|basename(clim)=="MIROC_rcp45_2040_2069"|basename(clim)=="MIROC_rcp85_2040_2069"|basename(clim)=="MPI_rcp45_2040_2069"){
        
        future_fog_fn <- paste0("G:/data/climate/MEInput/", scenario, "/", basename(clim), "/fog.asc")
      #Uncode write raster if you want the raster to be written
        #writeRaster(future_fog_4070_mask,future_fog_fn,format="ascii",overwrite=T)
        
      }else if (basename(clim)=="CCSM4_rcp85_2070_2099"|basename(clim)=="MIROC_rcp45_2070_2099"|basename(clim)=="MIROC_rcp85_2070_2099"|basename(clim)=="MPI_rcp45_2070_2099"){
        
        future_fog_fn <- paste0("G:/data/climate/MEInput/", scenario, "/", basename(clim), "/fog.asc")
      #Uncode write raster if you want the raster to be written
        #writeRaster(future_fog_70100_mask,future_fog_fn,format="ascii",overwrite=T)
        
      }else
      print ("No fog for this projection")
    }#End for loop through climate projections
}else
  print ("No Fog Data Available")



```



#Organization

```{r organization}

#Move files over to correct layer for MaxEnt and name them correctly

  clim_dirs<-list.dirs(path="G:/data/climate/GISModel_Input", full.names=T, recursive=F)
    for (clim in clim_dirs){
      #print (clim) #For loop through climate projections
      #Select files to pull from due to names set above
      #Which folders to pull from and send to for climate and fog variables
      clim_from<- paste0("G:/data/climate/MEInput/", scenario, "/", basename(clim), "/")
      clim_to<-paste0("G:/data/tools/MaxEnt/Input/", scenario, "/", basename(clim), "/layers/")
      
      #Which folders to pull from and send to for oak csv-just send to historic samples folders
      oak_from<-paste0("G:/data/islands/MaxEnt/MEInputOak/", scenario, "/OakPoints.csv")
      oak_to<-paste0("G:/data/tools/MaxEnt/Input/", scenario, "/historic/samples/OakPoints.csv")
      
      #Which folders to pull from and send to for island information-coded out because not sending unless needed
      #island_from<- paste0("G:/data/islands/MaxEnt/MEInput/", scenario, "/")
      #island_to<-paste0("G:/data/tools/MaxEnt/Input/", scenario, "/", basename(clim), "/layers/")
      
      files <- list.files(path = clim_from, pattern = ".asc$")
      for (i in files){
      var<-substr(i, 1, 3)
    #Uncode file copy if you want the files to be moved
      #file.copy(from=paste0(clim_from, i), to=paste0(clim_to,var, ".asc"), overwrite=TRUE)
      }#End climate move
      
      #Turn on if want to move over island variables
      #files <- list.files(path = island_from, pattern = ".asc$")
      #for (i in files){
      #file.copy(from=paste0(island_from, i), to=paste0(island_to,var, ".asc"), overwrite=TRUE)}
      
    }#End per climate
  #Oak points, because not dependent on climate projections
#Uncode file copy if you want the files to be moved
  #file.copy(from=oak_from, to=oak_to, overwrite=TRUE)


```

