---
title: "KrigingCatalina_AllBCM"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This R Markdown script can be used to interpolate the climate variables for Santa Catalina to the entire extent of the island, as the island is missing BCM climate data for some of its extent. The island DEM was used for universal co-kriging. The model for loops through the climate layers for current climate and all future climate projections and time periods, and saves the interpolated climate layers in a new folder for input into the ArcGIS data processing model. The layers were resampled to 270m, which can be selected in the script.

A big thanks to Allison Horst and her ESM 244 Data Analysis class for teaching us kriging.

```{r krige}

#Make sure all packages installed before running- use install.packages("packagename") if necessary
library(tidyverse) #datascience package
library(raster) #raster library
library(sf) #spatial
library(sp) #more spatial
library(gstat) #For geospatial statistics
library(rgdal) #spatial library 
library(dplyr) #data wrangling  
library(rgeos) #open source


#Define directories and files and pre-processing
########################################################################
#Bring in extent data to create spatial grid for Catalina
dsn_extent="G:/data/islands/sca/sca_extent" 
layer_extent="sca_extent"
CI_extent<-st_read(dsn = dsn_extent, layer = layer_extent)

#DEM in correct projections
DEM_sca<-raster("G:/data/islands/sca/DEM/sca_dem_alb/sca_dem_alb.tif") 

#Make CI extent into spatial points (Outline to raster to points for what to interpolate to)
ras <- raster()
extent(ras) <- extent(CI_extent)
CI_ras <- rasterize(CI_extent, ras, 'ShpAreaSqM')
proj4string(CI_ras)<-CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")

CI_ras_res<-raster("G:/data/islands/sca/sca_extent/scaext_alb270.tif")#resample for cell size 270x270
CI_resamp<-raster::resample(CI_ras, CI_ras_res)


CI_extent_points<-rasterToPoints(CI_resamp, spatial=FALSE)
CI_extent_points<-as.data.frame(CI_extent_points)

Grid <- subset(CI_extent_points, select=c(x,y))
colnames(Grid)<-c("Long", "Lat")
coordinates(Grid) <- ~ Long + Lat

# Make predictions over pixels (not single points)
gridded(Grid) = TRUE
proj4string(Grid) <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")

#Extract from DEM for the GRID
Grid_DEM<-raster::extract(DEM_sca, Grid)
Grid_sp<-Grid
Grid_sp$DEM<-Grid_DEM


#Time to For Loop through BCM variables
##########################################################

# dsn_bcm="G:/data/climate/GISModel_Input/historic/"
# files <- list.files(path = dsn_bcm, pattern = "\\.tif$")#From before f for loop-if only want to run one folder



folders<-list.dirs(path="G:/data/climate/GISModel_Input", recursive=FALSE)
for (f in folders){
dsn_bcm<-f
files <- list.files(path = dsn_bcm, pattern = "\\.tif$")
  for (c in files){
  BCM_ras <- raster(paste0(dsn_bcm,"/", c)) 
  BCM_ras_clip <- mask(BCM_ras, CI_extent) #Cut raster to bbox extent of islands
  
  BCM_points<-rasterToPoints(BCM_ras_clip, spatial=TRUE)#Create points from raster (using defined cell size)
  BCM_points<-as.data.frame(BCM_points)
  colnames(BCM_points)<-c("Avg", "lat", "long") #change x to long and y to lat
  coordinates(BCM_points) <- ~ lat + long #turns data int spatial points df
  proj4string(BCM_points) <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") #basically doing the same thing that crs did before
  
  BCM_DEM<-raster::extract(DEM_sca, BCM_points) #Pull DEM points using the raster BCM points
  BCM_sp<-BCM_points
  BCM_sp$DEM<-BCM_DEM  
  
  BCM_vg <- variogram(Avg ~ DEM, BCM_sp)#Create a variogram
  
  vg_fit <- fit.variogram(BCM_vg, vgm(c("Exp","Sph","Gau")))#Fit a variogram model
  
  BCM_krige <- krige(Avg ~ DEM, BCM_sp, newdata = Grid_sp, model = vg_fit)#Krige
  
  proj4string(BCM_krige)<-CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")
  
  writeGDAL(BCM_krige, fname=paste0("G:/data/climate/GIS_Input_SCAInterpolated/", basename(f), "/", c), drivername="GTiff")
  
  }#end c for loop
} #end f for loop


```

