---
title: "MaxEntAnalysisLooped"
author: "Sofie McComb"
date: "November 28, 2018"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown Script can be used to take the MaxEnt outputs and perform spatial and statistical analyses on the files for visualization in ArcGIS. The only variable you have to change is the scenario to the current scope of analysis being run. The script then for loops through all the current and projected climate file outputs for the scenario and performs the specified analyses for each and writes the appropriate raster tiff files to the correct folders. The entire process is automated so that a new scenario can be inputted and the all the same calculations and rasters can be created rapidly. Then the files can just be visualized in ArcGIS using predesigned templates for each analysis type that we created.


```{r scenario analysis}
##############################################################################
#Change the Scenario and the run the analysis

scenario<-"sca_int_270m"

#Options:
#allislands_270m
#ni_270m
#sca_270m
#sca_int_270m
#scr_270m
#sri_270m
#sri_adultyoung_270m
#sri_seedsap_270m
#scr_foginc_270m
#scr_fogdec_270m
#sri_foginc_270m
#sri_fogdec_270m
#scr_fogelev_270m
#sri_fogelev_270m
#scr_fogconstant_270m
#sri_fogconstant_270m
#MainlandCA

#Filename options:
filename<-"final2"

#Packages
library(tidyverse)#data rearrangement
library(raster)#rasters

#Note that rasters will overwrite themselves so run with caution or code them out
##############################################################################

#Grab model statistic values: Get AUC value from each climate run, but get threshold value from historic only

#Read in the csvs with the model statistics for that scenario for all climate projections
historic<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/historic/final2/maxentResults.csv"))
hist_2150<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/historic_1921_1950/final2/maxentResults.csv"))
hist_5180<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/historic_1951_1980/final2/maxentResults.csv"))

mpi45_1039<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/MPI_rcp45_2010_2039/final2/maxentResults.csv"))
mpi45_4069<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/MPI_rcp45_2040_2069/final2/maxentResults.csv"))
mpi45_7099<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/MPI_rcp45_2070_2099/final2/maxentResults.csv"))

ccsm485_1039<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/CCSM4_rcp85_2010_2039/final2/maxentResults.csv"))
ccsm485_4069<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/CCSM4_rcp85_2040_2069/final2/maxentResults.csv"))
ccsm485_7099<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/CCSM4_rcp85_2070_2099/final2/maxentResults.csv"))

miroc45_1039<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/MIROC_rcp45_2010_2039/final2/maxentResults.csv"))
miroc45_4069<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/MIROC_rcp45_2040_2069/final2/maxentResults.csv"))
miroc45_7099<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/MIROC_rcp45_2070_2099/final2/maxentResults.csv"))

miroc85_1039<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/MIROC_rcp85_2010_2039/final2/maxentResults.csv"))
miroc85_4069<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/MIROC_rcp85_2040_2069/final2/maxentResults.csv"))
miroc85_7099<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/MIROC_rcp85_2070_2099/final2/maxentResults.csv"))

#Select AUC values
hist_auc<-historic[101,] %>% 
  dplyr::select(Test.AUC)
hist_2150_auc<-hist_2150[101,] %>% 
  dplyr::select(Test.AUC)
hist_5180_auc<-hist_5180[101,] %>% 
  dplyr::select(Test.AUC)

mpi45_1039_auc<-mpi45_1039[101,] %>% 
  dplyr::select(Test.AUC)
mpi45_4069_auc<-mpi45_4069[101,] %>% 
  dplyr::select(Test.AUC)
mpi45_7099_auc<-mpi45_7099[101,] %>% 
  dplyr::select(Test.AUC)

ccsm485_1039_auc<-ccsm485_1039[101,] %>% 
  dplyr::select(Test.AUC)
ccsm485_4069_auc<-ccsm485_4069[101,] %>% 
  dplyr::select(Test.AUC)
ccsm485_7099_auc<-ccsm485_7099[101,] %>% 
  dplyr::select(Test.AUC)

miroc45_1039_auc<-miroc45_1039[101,] %>% 
  dplyr::select(Test.AUC)
miroc45_4069_auc<-miroc45_4069[101,] %>% 
  dplyr::select(Test.AUC)
miroc45_7099_auc<-miroc45_7099[101,] %>% 
  dplyr::select(Test.AUC)

miroc85_1039_auc<-miroc85_1039[101,] %>% 
  dplyr::select(Test.AUC)
miroc85_4069_auc<-miroc85_4069[101,] %>% 
  dplyr::select(Test.AUC)
miroc85_7099_auc<-miroc85_7099[101,] %>% 
  dplyr::select(Test.AUC)

#AUC Values for scenario
histTestAUC<-rbind(hist_auc, hist_2150_auc,hist_5180_auc) %>% 
  mutate(Projection=c("Historic", "Historic 1921_1950", "Historic 1951_1980")) %>% 
  dplyr::select(Projection, everything())

projTestAUC<-rbind(mpi45_1039_auc,mpi45_4069_auc,mpi45_7099_auc,
                   ccsm485_1039_auc,ccsm485_4069_auc,ccsm485_7099_auc,
                   miroc45_1039_auc,miroc45_4069_auc,miroc45_7099_auc,
                   miroc85_1039_auc,miroc85_4069_auc,miroc85_7099_auc) %>% 
  mutate(Projection=c("MPI 4.5 2010-2039", "MPI 4.5 2040-2069", "MPI 4.5 2070-2099",
                      "CCSM4 8.5 2010-2039", "CCSM4 8.5 2040-2069", "CCSM4 8.5 2070-2099",
                      "MIROC 4.5 2010-2039", "MIROC 4.5 2040-2069", "MIROC 4.5 2070-2099",
                      "MIROC 8.5 2010-2039", "MIROC 8.5 2040-2069", "MIROC 8.5 2070-2099")) %>% 
    dplyr::select(Projection, everything())

#Threshold value for scenario
#Threshold is the Binary threshold values:#Reclassify matrix based on 5 replicates average of the maximum training sensitivity + specifitiy (Liu 2013)
threshold<-historic[101,] %>% 
  dplyr::select(Maximum.training.sensitivity.plus.specificity.logistic.threshold)
threshold<-as.double(threshold)

#All statistic values gathered

########################################################
########################################################
########################################################
#Run the Analysis (should run smoothly based on inputs above)

#############################################################
#First part of analysis focused on raster analysis between historic and future projections
#############################################################
rclmat<-c(-Inf,threshold,0, threshold,1,1)#Actual reclassify matrix based on threshold
rclmat_grad<-c(-Inf,threshold,0)#Actual reclassify matrix based on threshold

#Run analysis on historic projections
historics<-c("historic", "historic_1921_1950", "historic_1951_1980")
histhighmat<-NULL
phistsuitmat<-NULL

for (h in historics){
  #Read in historic information
if (scenario=="MainlandCA"){
  hist<-raster(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/", h, "/", filename,"/Quercus_tomentella.asc"))
}else
  hist<-raster(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/", h, "/", filename,"/Quercus_tomentella_avg.asc"))


proj4string(hist) <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") 
writeRaster(hist, filename = paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/", h, ".tif"), format="GTiff", overwrite=TRUE)
histhigh<-cellStats(hist, max)
histhighmat<-rbind(histhighmat,histhigh)
histrc <- reclassify(hist, rclmat) #Threshold used here
writeRaster(histrc, filename = paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/", h, ".tif"), format="GTiff", overwrite=TRUE, datatype="INT1U")
histrc_grad <- reclassify(hist, rclmat_grad) #Threshold used here
writeRaster(histrc_grad, filename = paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary_gradient/", h, ".tif"), format="GTiff", overwrite=TRUE)
histfq<-as.data.frame(freq(histrc, 1))
histsuit<-histfq[2,2]
histnosuit<-histfq[1,2]
phistsuit<-histsuit/(histsuit+histnosuit)
phistsuitmat<-rbind(phistsuitmat, phistsuit)
} #end historic for loop

###Create historic summary table
histhighsuit<-as.data.frame(histhighmat,row.names = FALSE)
perchistsuit<-as.data.frame(phistsuitmat,row.names = FALSE)
histtable<-cbind(histTestAUC, histhighsuit, perchistsuit)
colnames(histtable)<-c("Projections", "Avg Test AUC", "Highest Present Suitability", "Percent Suitable Area")


#Run analysis on future projections
#Set historic for comparison code
if (scenario=="MainlandCA"){
  histpr<-raster(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/historic/", filename,"/Quercus_tomentella.asc"))
}else
  histpr<-raster(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/historic/", filename,"/Quercus_tomentella_avg.asc"))

proj4string(histpr) <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") 
histprrc <- reclassify(histpr, rclmat) #Threshold used here
histfq<-as.data.frame(freq(histprrc, 1))
histsuit<-histfq[2,2]
histnosuit<-histfq[1,2]



proj_nam<-as.matrix(c("MPI_rcp45_2010_2039", "MPI_rcp45_2040_2069", "MPI_rcp45_2070_2099","CCSM4_rcp85_2010_2039", "CCSM4_rcp85_2040_2069", "CCSM4_rcp85_2070_2099", "MIROC_rcp45_2010_2039", "MIROC_rcp45_2040_2069", "MIROC_rcp45_2070_2099", "MIROC_rcp85_2010_2039", "MIROC_rcp85_2040_2069", "MIROC_rcp85_2070_2099"))

highmat<-NULL
diffmeanmat<-NULL
diffmaxmat<-NULL
diffminmat<-NULL
pcsuitmat<-NULL
percsuitmat<-NULL

for (p in proj_nam){
print (p)
if (scenario=="MainlandCA"){
  proj<-raster(paste0("G:/data/tools/MaxEnt/Output/",scenario,"/",p,"/",filename,"/Quercus_tomentella_layers.asc"))
}else
  proj<-raster(paste0("G:/data/tools/MaxEnt/Output/",scenario,"/",p,"/",filename,"/Quercus_tomentella_layers_avg.asc"))
  

proj4string(proj) <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") 
writeRaster(proj, filename = paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/", p, ".tif"), format="GTiff", overwrite=TRUE)
high<-cellStats(proj, max)
highmat<-rbind(highmat,high)
diff<-proj-histpr
writeRaster(diff, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/", p, ".tif"), format="GTiff", overwrite=TRUE)
diffmean<-cellStats(diff, mean)
diffmeanmat<-rbind(diffmeanmat, diffmean)
diffmax<-cellStats(diff, max)
diffmaxmat<-rbind(diffmaxmat, diffmax)
diffmin<-cellStats(diff, min)
diffminmat<-rbind(diffminmat, diffmin)
projrc <- reclassify(proj, rclmat) #Threshold value used here
writeRaster(projrc, filename=paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/", p, ".tif"), format="GTiff", overwrite=TRUE, datatype="INT1U")
projrc_grad <- reclassify(proj, rclmat_grad) #Threshold value used here
writeRaster(projrc_grad, filename=paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary_gradient/", p, ".tif"), format="GTiff", overwrite=TRUE)
projfq<-as.data.frame(freq(projrc, 1))
projnosuit<-projfq[1,2]

if (nrow(projfq)==2){
  projsuit<-0
}else
  projsuit<-projfq[2,2]

###
pcsuit<-(projsuit-histsuit)/histsuit
pcsuitmat<-rbind(pcsuitmat, pcsuit)
percsuit<-projsuit/(projsuit+projnosuit)
percsuitmat<-rbind(percsuitmat, percsuit)


}#End proj names for loop


#Create projected summary table
highsuitdf<-as.data.frame(highmat,row.names = FALSE)
meandiffdf<-as.data.frame(diffmeanmat,row.names = FALSE)
gaindf<-as.data.frame(diffmaxmat,row.names = FALSE)
lossdf<-as.data.frame(diffminmat,row.names = FALSE)
pcsuitdf<-as.data.frame(pcsuitmat, row.names = FALSE)
percsuitdf<-as.data.frame(percsuitmat, row.names = FALSE)

projtable<-cbind(projTestAUC, highsuitdf, meandiffdf, gaindf, lossdf, percsuitdf, pcsuitdf)
colnames(projtable)<-c("Projections", "Avg Test AUC", "Highest Future Suitability", "Mean Change in Suitability", "Highest Gain", "Highest Loss","Percent Suitable Area", "Overall Percent Change of Suitable Area")


#Export tables for histtable and projtable
write.csv(histtable,file=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/summarytables/historicsummarytable.csv"),row.names = FALSE)
write.csv(projtable,file=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/summarytables/projectionssummarytable.csv"),row.names = FALSE)

#############################################################
#Second part of analysis focused on raster analysis between all stacked rasters
#############################################################

#Read in all rasters and create summed raster (ignoring other historic options here)
histrc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/historic.tif"))
projA1rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MPI_rcp45_2010_2039.tif"))
projA2rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MPI_rcp45_2040_2069.tif"))
projA3rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MPI_rcp45_2070_2099.tif"))
projB1rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/CCSM4_rcp85_2010_2039.tif"))
projB2rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/CCSM4_rcp85_2040_2069.tif"))
projB3rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/CCSM4_rcp85_2070_2099.tif"))
projC1rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp45_2010_2039.tif"))
projC2rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp45_2040_2069.tif"))
projC3rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp45_2070_2099.tif"))
projD1rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp85_2010_2039.tif"))
projD2rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp85_2040_2069.tif"))
projD3rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp85_2070_2099.tif"))

  #Sum across scenarios and write raster
Asum<-sum(histrc, projA1rc, projA2rc, projA3rc)
writeRaster(Asum, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/percentchange/MPI_rcp45.tif"), format="GTiff", overwrite=TRUE)
Bsum<-sum(histrc, projB1rc, projB2rc, projB3rc)
writeRaster(Bsum, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/percentchange/CCSM4_rcp85.tif"), format="GTiff", overwrite=TRUE)
Csum<-sum(histrc, projC1rc, projC2rc, projC3rc)
writeRaster(Csum, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/percentchange/MIROC_rcp45.tif"), format="GTiff", overwrite=TRUE)
Dsum<-sum(histrc, projD1rc, projD2rc, projD3rc)
writeRaster(Dsum, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/percentchange/MIROC_rcp85.tif"), format="GTiff", overwrite=TRUE)

#Sum all and write raster
Allsum<-sum(histrc, projA1rc, projA2rc, projA3rc, projB1rc, projB2rc, projB3rc, projC1rc, projC2rc, projC3rc, projD1rc, projD2rc, projD3rc)
writeRaster(Allsum, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/percentchange/ALLScenarios.tif"), format="GTiff", overwrite=TRUE)


```

