---
title: "MaxEnt Toolbox"
author: "Oakology"
date: "January 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Scenario Selection

#Otherwise can run through all the scenarios at once using the scenario for loop in each section. If choosing scenario selection make sure to turn off scenario for loops in each section by commenting them out.

```{r extent_selection}

#Change scenario- one thing to change throughout
scenario<-"allislands_270m"

#Options:
#allislands_270m
#ni_270m
#sca_270m
#sca_int_270m
#scr_270m
#sri_270m
#sri_adultyoung_270m
#sri_seedsap_270m
#scr_foginc_270m
#scr_fogdec_270m
#sri_foginc_270m
#sri_fogdec_270m
#scr_fogelev_270m
#sri_fogelev_270m
#MainlandCA



```

#Should create a section to make a new scenario and add needed folders?

Load Packages

```{r packages, message=FALSE}

#If packages missing use install.packages("packagename")
library(tidyverse)
library(sf)
library(raster)
library(sp)
library(rgdal)
library(tools)
#library(maptools)
#library(dismo)

```


Extent

```{r extent}

#Create scenario extent that will be used throughout the rest of the processes, based off the minimum BCM data available as well as the Channel Island CUSP outlines

scen<-c("allislands_270m","ni_270m","sca_270m","sca_int_270m","scr_270m","sri_270m","sri_adultyoung_270m","sri_seedsap_270m","scr_foginc_270m","scr_fogdec_270m","sri_foginc_270m","sri_fogdec_270m","scr_fogelev_270m","sri_fogelev_270m","MainlandCA")

#If want to run all scenarios at once
for (s in scen){
print (s)
scenario<-s

#If else statements for scenarios: read in the correct data for each scenario
if (scenario=="allislands_270m"){
  #All Islands
  scenario_extent<-read_sf("G:/data/islands/all_islands/extent/allislandsoutline.shp")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="ni_270m"){
  #Northern Islands
  scenario_extent<-read_sf("G:/data/islands/all_islands/ni_outline/ni_outline.shp")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="scr_270m"|scenario=="scr_foginc_270m"|scenario=="scr_fogdec_270m"|scenario=="scr_fogelev_270m"){
  #Santa Cruz
  scenario_extent<-read_sf("G:/data/islands/scr/scr_extent/scr_extent.shp")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="sri_270m"|scenario=="sri_adultyoung_270m"|scenario=="sri_seedsap_270m"|scenario=="sri_foginc_270m"|scenario=="sri_fogdec_270m"|scenario=="sri_fogelev_270m"){
  #Santa Rosa
  scenario_extent<-read_sf("G:/data/islands/sri/sri_extent/sri_extent.shp")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="sca_270m"){
  #Santa Catalina
  scenario_extent<-read_sf("G:/data/islands/sca/sca_extent/sca_extent.shp")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="sca_int_270m"){
  #Santa Catalina Interpolated
  scenario_extent<-read_sf("G:/data/islands/sca/sca_extent/sca_extent.shp")
  min_data<-raster("G:/data/climate/GIS_Input_SCAInterpolated/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else if (scenario=="MainlandCA"){
  #Mainland CA
  scenario_extent<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
  min_data<-raster("G:/data/climate/GISModel_Input/historic/cwd1981_2010_ave_HST_1539127145.tif")
}else
  print ("No Scenario Selected")

cropped <- crop(min_data, extent(scenario_extent)) #Crop to extent of outlines
scen_extent <- mask(cropped, scenario_extent) #Mask to the exact island outline(s)
extent(scen_extent)<-round(extent(scen_extent),1) #Rerun with rounded extent so extents same decimal amount
writeRaster(scen_extent, filename=paste0("G:/data/islands/MaxEnt/Extent/", scenario, ".tif"), overwrite=TRUE)#write extent raster

}#To run all scenarios at once. Comment out if running scenario by scenario

#Extent will be used throughout Script. Will call in the extent each time just to be careful.

```


Oak Combined and Individual 

***RUN THIS CODE ONCE SRI OAKS REPLACED

```{r oakpoints}

#Read in Oak Points
sca_oaks<-read_sf("G:/data/islands/sca/Quertome/SCAOakPoints_AEA.shp")
sca_xy<-st_coordinates(sca_oaks)
sri_oaks<-read_sf("G:/data/islands/sri/OakPoint/SRI_OakPoints_Updated.shp")#Fix so correct points
sri_xy<-st_coordinates(sri_oaks)
scr_oaks<-read_sf("G:/data/islands/scr/OakPoint/SCR_OakPoints_Updated.shp")
scr_xy<-st_coordinates(scr_oaks)


scen<-c("allislands_270m","ni_270m","sca_270m","sca_int_270m","scr_270m","sri_270m","sri_adultyoung_270m","sri_seedsap_270m","scr_foginc_270m","scr_fogdec_270m","sri_foginc_270m","sri_fogdec_270m","scr_fogelev_270m","sri_fogelev_270m","MainlandCA")

#If want to run all scenarios at once
for (s in scen){
print (s)
scenario<-s

#If else statements for scenarios: read in the correct data for each scenario
if (scenario=="allislands_270m"|scenario=="MainlandCA"){
  #All Islands or Mainland CA
  all_oaks<-rbind(sca_xy[,1:2],sri_xy[,1:2],scr_xy[,1:2])
}else if (scenario=="ni_270m"){
  #Northern Islands
 all_oaks<-rbind(sri_xy[,1:2],scr_xy[,1:2])
}else if (scenario=="scr_270m"|scenario=="scr_foginc_270m"|scenario=="scr_fogdec_270m"){
  #Santa Cruz
all_oaks<-scr_xy[,1:2]
}else if (scenario=="sri_270m"|scenario=="sri_foginc_270m"|scenario=="sri_fogdec_270m"){
  #Santa Rosa
all_oaks<-sri_xy[,1:2]
}else if (scenario=="sca_270m"|scenario=="sca_int_270m"){
  #Santa Catalina and Santa Catalina Interpolated
all_oaks<-sca_xy[,1:2]
}else if (scenario=="sri_adultyoung_270m"){
  #Santa Rosa Adult and Young
sri_ay<-subset(sri_oaks, sri_oaks$Age=="adult"|sri_oaks$Age=="young") #Fix this so it works
sri_xy<-st_coordinates(sri_ay)
all_oaks<-sri_xy[,1:2]
}else if (scenario=="sri_seedsap_270m"){
  #Santa Rosa Seedling and Saplings
sri_ay<-subset(sri_oaks, sri_oaks$Age=="seedling"|sri_oaks$Age=="sapling") #Fix this so it works
sri_xy<-st_coordinates(sri_ay)
all_oaks<-sri_xy[,1:2]
}else
  print ("No Scenario Selected")

#Make Oak Point CSV based on selected oak points
alloaks<-as.data.frame(all_oaks)
alloaks$Species<-"Quercus tomentella"
Oaks<-alloaks[,c(3,1,2)]
oak_fn<-paste0("G:/data/islands/MaxEnt/MEInputOak/", scenario,"/OakPoints.csv")
write.csv(Oaks, oak_fn, row.names=FALSE)

}#To run all scenarios at once. Comment out if running scenario by scenario


```



Climate  
#Running in shell

```{r}

scen<-c("allislands_270m","ni_270m","sca_270m","sca_int_270m","scr_270m","sri_270m","sri_adultyoung_270m","sri_seedsap_270m","scr_foginc_270m","scr_fogdec_270m","sri_foginc_270m","sri_fogdec_270m","scr_fogelev_270m","sri_fogelev_270m","MainlandCA")

#If want to run all scenarios at once
for (s in scen){
print (s)
scenario<-s

if (scenario=="sca_int_270m"){
  #Santa Catalina Interpolated: Made by KrigingCatalina_AllBCM.Rmd
  clim_dirs<-list.dirs(path="G:/data/climate/GIS_Input_SCAInterpolated", full.names=F, recursive=F)
}else
clim_dirs<-list.dirs(path="G:/data/climate/GISModel_Input", full.names=T, recursive=F)

#Call in appropriate extent
scen_extent<-raster(paste0("G:/data/islands/MaxEnt/Extent/", scenario, ".tif"))
crs(scen_extent)<-CRS('+init=epsg:3310') 
 
for (clim in clim_dirs){
  print (clim) #For loop through climate projections
  clim_vars<-list.files(clim, pattern='tif$', full.names=TRUE )
  for (var in clim_vars){
    print (var)#For loop through climate variables
    clim_ras<-raster(var)
    crs(clim_ras)<-CRS('+init=epsg:3310')
    clim_crop <- crop(clim_ras, extent(scen_extent)) #Crop to extent of outlines
    climate <- mask(clim_crop, scen_extent) #Mask to the exact island outline(s)
    extent(climate)<-round(extent(climate),1) #Rerun with rounded extent so extents same decimal amount
    fn <- paste0("G:/data/climate/MEInput/", scenario, "/", basename(clim), "/", file_path_sans_ext(basename(var)), ".asc")
    writeRaster(climate,fn,format="ascii",overwrite=T)
  }#End for loop through climate variables
}#End for loop through climate projections

}#To run all scenarios at once. Comment out if running scenario by scenario

```



Island
#Need to finish up DEM issues, calculate slope and aspect, and then run all of these for each scenario 

```{r}

scen<-c("allislands_270m","ni_270m","sca_270m","sca_int_270m","scr_270m","sri_270m","sri_adultyoung_270m","sri_seedsap_270m","scr_foginc_270m","scr_fogdec_270m","sri_foginc_270m","sri_fogdec_270m","scr_fogelev_270m","sri_fogelev_270m","MainlandCA")

#If want to run all scenarios at once
for (s in scen){
print (s)
scenario<-s

#For MainlandCA set this all to NULL

#Set final directory
island_fn<-paste0("G:/data/islands/MaxEnt/MEInput/", scenario, "/")
#Call in appropriate extent
scen_extent<-raster(paste0("G:/data/islands/MaxEnt/Extent/", scenario, ".tif"))
crs(scen_extent)<-CRS('+init=epsg:3310') 


#Soils
  soilshp<-read_sf("G:/data/islands/all_islands/Soil/soils_AEA.shp")
  ext<-extent(scen_extent)
  gridsize <- 270
  soilr <- raster(ext, res=gridsize)
  soilras <- rasterize(soilshp, soilr, field = 'MapUnit')
  crs(soilras)<-CRS('+init=epsg:3310')
  soil_crop <- crop(soilras, extent(scen_extent)) #Crop to extent of outlines
  soils <- mask(soil_crop, scen_extent) #Mask to the exact island outline(s)
  writeRaster(soils,paste0(island_fn, "soilclasses.asc"),format="ascii",overwrite=T)
  

#Vegetation: Made by VegetationMapGrouping.Rmd
  #SCR
    scr_vegpshp<-read_sf("G:/data/islands/scr/SCRVegMapClass/SCRVegMapClass.shp")
    scr_vegr <- raster(extent(scen_extent), res=270)
    scr_vegras <- rasterize(scr_vegpshp, scr_vegr, field = 'Value')
    crs(scr_vegras)<-CRS('+init=epsg:3310')
  #NI
    ni_vegpshp<-read_sf("G:/data/islands/all_islands/Channel_Islands_Veg_Map_2017/NIVegMapClass/NIVegMapClass.shp")
    ni_vegr <- raster(extent(scen_extent), res=270)
    ni_vegras <- rasterize(ni_vegpshp, ni_vegr, field = 'Value')
    crs(ni_vegras)<-CRS('+init=epsg:3310')
  #SCA
    sca_vegpshp<-read_sf("G:/data/islands/sca/SCAVegMapClass/SCAVegMapClass.shp")
    sca_vegr <- raster(extent(scen_extent), res=270)
    sca_vegras <- rasterize(sca_vegpshp, sca_vegr, field = 'Value')
    crs(sca_vegras)<-CRS('+init=epsg:3310')
  #Merge to New Raster
    all_veg<-merge(scr_vegras, ni_vegras, sca_vegras)
    veg_crop <- crop(all_veg, extent(scen_extent)) #Crop to extent of outlines
    veg <- mask(veg_crop, scen_extent) #Mask to the exact island outline(s)
    writeRaster(veg,paste0(island_fn, "veg.asc"),format="ascii",overwrite=T)
    
    
#DEM THE STRUGGLE-Come back and fix
  ai_dem<-raster("G:/data/islands/all_islands/DEM/ai_dem270.tif")
  scr_dem<-raster("G:/data/islands/all_islands/DEM/scr_dem270.tif")
  sri_dem<-raster("G:/data/islands/all_islands/DEM/sri_dem270.tif")
  smi_dem<-raster("G:/data/islands/all_islands/DEM/smi_dem270.tif")
  sca_dem<-raster("G:/data/islands/sca/DEM/sca_dem_alb/sca_dem_alb270.tif")
  all_dem<-merge(ai_dem, scr_dem, sri_dem, smi_dem, sca_dem, tolerance=0.5)#Accepts different origins
  #all_dem<-raster("G:/data/islands/all_islands/DEM/all_dem270.tif") #Combined all DEMS at 270 in GIS with mosaic to new raster because much quicker and save across all projects
  crs(all_dem)<-CRS('+init=epsg:3310')
  #Figure out cropping and masking issue 
  dem_crop <- crop(all_dem, scen_extent) #Crop to extent of outlines
  dem <- mask(dem_crop, scen_extent) #Mask to the exact island outline(s)
  writeRaster(dem,paste0(island_fn, "DEM.asc"),format="ascii",overwrite=T)

  #Slope
  all_terrain<-terrain(all_dem, opt=c('slope', 'aspect'), unit='degrees')
  writeRaster(Slope,paste0(island_fn, "Slope.asc"),format="ascii",overwrite=T)
#Aspect
  writeRaster(Aspect,paste0(island_fn, "Aspect.asc"),format="ascii",overwrite=T)

}#To run all scenarios at once. Comment out if running scenario by scenario
  
```



Fog

```{r}


scen<-c("allislands_270m","ni_270m","sca_270m","sca_int_270m","scr_270m","sri_270m","sri_adultyoung_270m","sri_seedsap_270m","scr_foginc_270m","scr_fogdec_270m","sri_foginc_270m","sri_fogdec_270m","scr_fogelev_270m","sri_fogelev_270m","MainlandCA")

#If want to run all scenarios at once
for (s in scen){
print (s)
scenario<-s

scen_extent<-raster(paste0("G:/data/islands/MaxEnt/Extent/", scenario, ".tif"))
crs(scen_extent)<-CRS('+init=epsg:3310') 

#If else statements for scenarios: read in the correct data for each scenario
if (scenario=="scr_foginc_270m"){
  #Future fog changed by a percent (20%) Inc/Dec for SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/scr_allfog_270.tif")
  future_fog<-raster("G:/data/climate/Fog/Fog_270/PercentChange/scr_all_increase20_270.tif")
  
}else if (scenario=="scr_fogdec_270m"){
  #Future fog changed by a percent (20%) Inc/Dec for SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/scr_allfog_270.tif")
  future_fog<-raster("G:/data/climate/Fog/Fog_270/PercentChange/scr_all_decrease20_270.tif")

}else if (scenario=="sri_foginc_270m"){
  #Future fog changed by a percent (20%) Inc/Dec for SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/sri_allfog_270.tif")
  future_fog<-raster("G:/data/climate/Fog/Fog_270/PercentChange/sri_all_increase20_270.tif")

}else if (scenario=="sri_fogdec_270m"){
  #Future fog changed by a percent (20%) Inc/Dec for SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/sri_allfog_270.tif")
  future_fog<-raster("G:/data/climate/Fog/Fog_270/PercentChange/sri_all_decrease20_270.tif")

}else if (scenario=="scr_fogelev_270m"){
  #Future Fog Elevation (+-20%): SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/scr_allfog_270.tif")
  future_fog<-raster("G:/data/climate/Fog/Fog_270/Elevation/scr_all_elevation20.tif")
  
}else if (scenario=="sri_fogelev_270m"){
  #Future Fog Elevation (+-20%): SRI and SCR
  current_fog<-raster("G:/data/climate/Fog/Fog_270/Historic/sri_allfog_270.tif")
  future_fog<-raster("G:/data/climate/Fog/Fog_270/Elevation/sri_all_elevation20.tif")

}else
  print ("No Fog Data Available")




if (scenario=="scr_foginc_270m"|scenario=="scr_fogdec_270m"|scenario=="sri_foginc_270m"|scenario=="sri_fogdec_270m"|scenario=="scr_fogelev_270m"|scenario=="sri_fogelev_270m"){
  
#Have to write a code that goes through the climate folders and inserts current into historic and 
  
  extent(current_fog)<-round(extent(current_fog),1)
  extent(future_fog)<-round(extent(future_fog),1)
  current_fog_crop <- crop(current_fog, scen_extent) #Crop to extent of outlines
  current_fog_mask <- mask(current_fog_crop, scen_extent) #Mask to the exact island outline(s)
  future_fog_crop <- crop(future_fog, scen_extent) #Crop to extent of outlines
  future_fog_mask <- mask(future_fog_crop, scen_extent) #Mask to the exact island outline(s)
  
  
  clim_dirs<-list.dirs(path="G:/data/climate/GISModel_Input", full.names=T, recursive=F)
    for (clim in clim_dirs){
      #print (clim) #For loop through climate projections
      current_fog_fn <- paste0("G:/data/climate/MEInput/", scenario, "/", basename(clim), "/currentfog.asc")
      writeRaster(current_fog_mask,current_fog_fn,format="ascii",overwrite=T)
      future_fog_fn <- paste0("G:/data/climate/MEInput/", scenario, "/", basename(clim), "/futurefog.asc")
      writeRaster(future_fog_mask,future_fog_fn,format="ascii",overwrite=T)
    }#End for loop through climate projections
}else
  print ("No Fog Data Available")

}#To run all scenarios at once. Comment out if running scenario by scenario

```



Organization

```{r}

#Copy over code from BCM_organization but add in for all options made above but can select which of the variables actually should be carried over based on our decisions
#And based on scenario-some have fog and others dont and difference in oak points



```

