---
title: "MaxEntAnalysisLooped"
author: "Sofie McComb"
date: "November 28, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown Script can be used to take the MaxEnt outputs and perform spatial and statistical analyses on the files for visualization in ArcGIS. The only variable you have to change is the scenario to the current scope of analysis being run, as well as add in any important AUC or binary threshold information for each scenario. The script then for loops through all the current and projected climate file outputs for the scenario and performs the specified analyses for each and writes the appropriate raster tiff files to the correct folders. The entire process is automated so that a new scenario can be inputted and the all the same calculations and rasters can be created rapidly. Then the files can just be visualized in ArcGIS using predesigned templates for each analysis type that we created.

```{r}
######################################################
#Pick and choose analysis adventure

###CHANGE THIS VARIABLE AND THE REST IS MAGIC (all based on scenario option)
scenario<-"allCA"

#Options:
#allislands_270m
#ni_270m
#sca_270m
#sca_int_270m
#scr_270m
#sri_270m
#sri_adultyoung_270m
#sri_seedsap_270m
#scr_foginc_270m
#scr_fogdec_270m
#sri_foginc_270m
#sri_fogdec_270m
#scr_fogelev_270m
#sri_fogelev_270m
#scr_fogconstant_270m
#sri_fogconstant_270m
#MainlandCA

#Note that rasters will overwrite themselves so run with caution or code them out

###################################
#THESE VARIABLES WILL NOW BE SELECTED BASED ON SCENARIO OPTION

#Threshold is the Binary threshold values:#Reclassify matrix based on 5 replicates average of the maximum training sensitivity + specifitiy (Liu 2013)
#Order of AUC is MPI 4.5, CCSM4 8.5, MIROC 4.5, MIROC 8.5
#Often Test AUC for Each Island Sensitive to Replicates and Selected Test Data

#Change this so that it it pulling in the csv and reading the column values

# Need to change htat instead by scenario its by the projection type as well- go through all scenarios and projections and read in the csv in that folder and pull out the threshold value and average AUC value
#Make sure all the scenario folders are made

hist<-read.csv(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/historic/final/csvname.csv"))

if (scenario=="allislands_100m"){
  threshold<- 0.274
  histAUC<-0.824
  AvgTestAUC<-as.data.frame(c(0.874, 0.896, 0.828, 0.875, 0.883, 0.864, 0.881, 0.779, 0.847, 0.867, 0.904, 0.866))
} else if (scenario=="sca_int_100m"){
  threshold<- 0.423
  histAUC<-0.835
  AvgTestAUC<-as.data.frame(c(0.715, 0.674, 0.767, 0.733, 0.756, 0.704, 0.605, 0.690, 0.719, 0.708, 0.681, 0.804))
} else if (scenario=="sri_100m"){
  threshold<- 0.240
  histAUC<-0.980
  AvgTestAUC<-as.data.frame(c(0.981, 0.985, 0.935, 0.844, 0.809, 0.922, 0.848, 0.896, 0.912, 0.979, 0.985, 0.945))
} else if (scenario=="sri_100m_adultyoung"){
  threshold<- 0.346
  histAUC<-0.820
  AvgTestAUC<-as.data.frame(c(0.987, 0.994, 0.810, 0.815, 0.997, 0.990, 0.983, 0.901, 0.985, 0.808, 0.982, 0.906))
} else if (scenario=="sri_100m_seedling"){
  threshold<- 0.208
  histAUC<-0.993
  AvgTestAUC<-as.data.frame(c(0.987, 0.981, 0.802, 0.985, 0.988, 0.995, 0.996, 0.984, 0.988, 0.983, 0.996, 0.997))
} else if(scenario=="sri_100m_seedlingsapling"){
  threshold<- 0.212
  histAUC<-0.996
  AvgTestAUC<-as.data.frame(c(0.986, 0.900, 0.996, 0.968, 0.988, 0.810, 0.996, 0.801, 0.980, 0.803, 0.984, 0.997))
} else if(scenario=="allCA"){
  threshold<- 0.061
  histAUC<-0.992
  AvgTestAUC<-as.data.frame(c(0.997, 0.994, 0.995, 0.993, 0.995, 0.994, 0.991, 0.995, 0.992, 0.997, 0.991, 0.993))
} else {
  NULL
}


filename<-"final"
#filename options: #final (to be used for all but option is there)

########################################################
########################################################
########################################################
#This should all run smoothly based on inputs above

library(raster)
library(gdata)#for combine function

rclmat<-c(-Inf,threshold,0, threshold,1,1)#Actual reclassify matrix based on threshold

#Read in historic information
hist<-raster(paste0("G:/data/tools/MaxEnt/Output/", scenario, "/historic/final/quercus_tomentella.asc"))
proj4string(hist) <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") 
writeRaster(hist, filename = paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/historic.tif"), format="GTiff", overwrite=TRUE)
histhigh<-cellStats(hist, max)
histrc <- reclassify(hist, rclmat)
writeRaster(histrc, filename = paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/historic.tif"), format="GTiff", overwrite=TRUE)
histfq<-as.data.frame(freq(histrc, 1))
histsuit<-histfq[2,2]

proj_nam<-as.matrix(c("MPI_rcp45_2010_2039", "MPI_rcp45_2040_2069", "MPI_rcp45_2070_2099","CCSM4_rcp85_2010_2039", "CCSM4_rcp85_2040_2069", "CCSM4_rcp85_2070_2099", "MIROC_rcp45_2010_2039", "MIROC_rcp45_2040_2069", "MIROC_rcp45_2070_2099", "MIROC_rcp85_2010_2039", "MIROC_rcp85_2040_2069", "MIROC_rcp85_2070_2099"))

highmat<-NULL
diffmeanmat<-NULL
diffmaxmat<-NULL
diffminmat<-NULL
pcsuitmat<-NULL

for (p in proj_nam){
print (p)
proj<-raster(paste0("G:/data/tools/MaxEnt/Output/",scenario,"/",p,"/",filename,"/quercus_tomentella.asc"))
proj4string(proj) <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") 
writeRaster(proj, filename = paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/", p, ".tif"), format="GTiff", overwrite=TRUE)
high<-cellStats(proj, max)
highmat<-rbind(highmat,high)
diff<-proj-hist
writeRaster(diff, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/", p, ".tif"), format="GTiff", overwrite=TRUE)
diffmean<-cellStats(diff, mean)
diffmeanmat<-rbind(diffmeanmat, diffmean)
diffmax<-cellStats(diff, max)
diffmaxmat<-rbind(diffmaxmat, diffmax)
diffmin<-cellStats(diff, min)
diffminmat<-rbind(diffminmat, diffmin)
projrc <- reclassify(proj, rclmat)
writeRaster(projrc, filename=paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/", p, ".tif"), format="GTiff", overwrite=TRUE)
projfq<-as.data.frame(freq(projrc, 1))
projsuit<-projfq[2,2]
pcsuit<-(projsuit-histsuit)/histsuit
pcsuitmat<-rbind(pcsuitmat, pcsuit)
}



###Create summary tables
#Historic
histtable <- as.data.frame(matrix(0, ncol = 2, nrow = 1))
colnames(histtable)<-c("Avg Test AUC", "Highest Present Suitability")
histtable[1,1]<-histAUC
histtable[1,2]<-histhigh

#Projections
#combine all the names together as column
projections<-as.data.frame(c("MPI_rcp45_2010_2039", "MPI_rcp45_2040_2069", "MPI_rcp45_2070_2099","CCSM4_rcp85_2010_2039", "CCSM4_rcp85_2040_2069", "CCSM4_rcp85_2070_2099", "MIROC_rcp45_2010_2039", "MIROC_rcp45_2040_2069", "MIROC_rcp45_2070_2099", "MIROC_rcp85_2010_2039", "MIROC_rcp85_2040_2069", "MIROC_rcp85_2070_2099"))
colnames(projections)<-"Projections"


highsuit<-as.data.frame(highmat,row.names = FALSE)
meandiff<-as.data.frame(diffmeanmat,row.names = FALSE)
gain<-as.data.frame(diffmaxmat,row.names = FALSE)
loss<-as.data.frame(diffminmat,row.names = FALSE)
pcsuit<-as.data.frame(pcsuitmat, row.names = FALSE)

colnames(AvgTestAUC)<-"AvgTestAUC" 

projtable<-cbind(projections, AvgTestAUC, highsuit, meandiff, gain, loss, pcsuit)
colnames(projtable)<-c("Projections", "Avg Test AUC", "Highest Future Suitability", "Mean Change in Suitability", "Highest Gain", "Highest Loss", "Overall Percent Change of Suitable Area")


#Export tables for histtable and projtable
write.csv(histtable,file=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/summarytables/historicsummarytable.csv"),row.names = FALSE)
write.csv(projtable,file=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/summarytables/projectionssummarytable.csv"),row.names = FALSE)

#Read in all rasters and create summed raster
histrc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/historic.tif"))
projA1rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MPI_rcp45_2010_2039.tif"))
projA2rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MPI_rcp45_2040_2069.tif"))
projA3rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MPI_rcp45_2070_2099.tif"))
projB1rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/CCSM4_rcp85_2010_2039.tif"))
projB2rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/CCSM4_rcp85_2040_2069.tif"))
projB3rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/CCSM4_rcp85_2070_2099.tif"))
projC1rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp45_2010_2039.tif"))
projC2rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp45_2040_2069.tif"))
projC3rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp45_2070_2099.tif"))
projD1rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp85_2010_2039.tif"))
projD2rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp85_2040_2069.tif"))
projD3rc<-raster(paste0("G:/data/tools/MaxEnt/Output_tiff/", scenario, "/binary/MIROC_rcp85_2070_2099.tif"))

  #Sum across scenarios and write raster
Asum<-sum(histrc, projA1rc, projA2rc, projA3rc)
writeRaster(Asum, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/percentchange/MPI_rcp45.tif"), format="GTiff", overwrite=TRUE)
Bsum<-sum(histrc, projB1rc, projB2rc, projB3rc)
writeRaster(Bsum, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/percentchange/CCSM4_rcp85.tif"), format="GTiff", overwrite=TRUE)
Csum<-sum(histrc, projC1rc, projC2rc, projC3rc)
writeRaster(Csum, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/percentchange/MIROC_rcp45.tif"), format="GTiff", overwrite=TRUE)
Dsum<-sum(histrc, projD1rc, projD2rc, projD3rc)
writeRaster(Dsum, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/percentchange/MIROC_rcp85.tif"), format="GTiff", overwrite=TRUE)

#Sum all and write raster
Allsum<-sum(histrc, projA1rc, projA2rc, projA3rc, projB1rc, projB2rc, projB3rc, projC1rc, projC2rc, projC3rc, projD1rc, projD2rc, projD3rc)
writeRaster(Allsum, filename=paste0("G:/data/tools/MaxEnt/Analysis/", scenario, "/percentchange/ALLScenarios.tif"), format="GTiff", overwrite=TRUE)



```

